\subsection{{Homelab \hfill}}
\subtext{Home servers used for learning purposes. \hfill}
\begin{zitemize}
\item DroneCI - Build server utilizing Docker containers for CI/CD of various applications.
\item Portainer - Docker management system for easy deployment and maintenance of containerized applications.
\item Gitea - Self-Hosted Git version control system, used in conjunction with hosted storage to perform version control of game development assets.
\item Minio - Self-Hosted S3 compatible object storage system, used for Git LFS.
\end{zitemize}

\subsection{{Hackathons \hfill}}
\subtext{24-hour technology competitions. Developed software with teams either for fun or to solve a problem. As 
organizer, arranged event catering and scheduled events. \hfill}
\begin{zitemize}
\item \textbf{Revolution UC} (Spring 2014) - Developed a mobile application using text to speech that converts spoken code into written code.
\item \textbf{Revolution UC} (Fall 2014) - Helped organize the event and assisted students during the event as needed.
\item \textbf{Revolution UC} (Spring 2015) - Created a VR Legend of Zelda experience using Unity that incorporated motion control via Myo wristbands. The project won best use of wearable tech.
\item \textbf{AngelHack} - Developed a node.js web application designed to allow local owners of 3D printers to sell printer time to users looking for items to print.
\item \textbf{HackOTR} (March 2015) - Developed an Android application for aggregating user media suggestions from friends and allowing rating and ranking of suggestions.
\item \textbf{HackOTR} (August 2015) - Developed a node.js application that provided a tinder style interface for purchasing homes using Casamatic data. Project won best use of Casamatic data and 1st place.
\end{zitemize}


