%====================
% EXPERIENCE A
%====================
\subsection{{Software Engineer \hfill JUN 2024 --- Present}}
\subtext{Johnson \& Johnson MedTech \hfill Cincinnati, Ohio}
\begin{zitemize}
\item Devloped Web Platform for User Authentication and Access to Data
\item Developed Clinical Video Overlay Application
\item Performed Lab Support Duties as Needed for Robotic Test Hardware
\item Developed Monitoring for Robotic Testing Platform to Investigate Hardware Errors
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{{Software Engineer, Onsite Services - Ethicon \hfill AUG 2023 --- Present}}
\subtext{Kaleidoscope Innovation \hfill Cincinnati, Ohio}
\begin{zitemize}
\item Developed Surgical Robotics Testing Platform utilizing ROS and Python
\item Developed Staple Image Analysis Application in Python
\item Developed Raspberry Pi Streaming Camera Setup utilizing OpenCV and Python
\end{zitemize}

%====================
% EXPERIENCE A
%====================
\subsection{{Client Technical Marketing Engineer \hfill MAR 2021 --- AUG 2023}}
\subtext{Intel Corporation \hfill Florence, Kentucky}
\begin{zitemize}
\item Enhanced PowerShell automation around benchmarking of hardware.
\item Tested various scenarios to find wins vs. competing hardware on Windows and Linux.
\item Performed pathfinding to determine ideal testing scenarios for competitive analysis.
\item Developed stock tracking application for visualization of GPU sales in ASP.NET Core.
\item Developed Data collection and visualization application for collected testing data.
\item Managed and engaged with Intel Community Discord and internal source communities.
\item Developed applications that ran on Linux platforms.
\item Utilized Linux to develop automation for hardware testing.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Site Reliability Engineer I, II \hfill JAN 2017 --- MAR 2021}}
\subtext{Myriad Neuroscience \hfill Mason, Ohio}
\begin{zitemize}
\item Wrote PowerShell scripts for continuous integration via TeamCity.
\item Facilitated deployment of ASP.NET and .NET Core Web applications to IIS.
\item Performed manual schema changes and database migrations on SQL databases.
\item Interacted with internal and external end user support tickets to investigate and triage issues within production systems.
\item Investigated deployment of GeneSight applications to Linux Operating systems.
\item Managed Apache configurations for TeamCity server.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Software Engineer I \hfill MAY 2016 --- JAN 2017}}
\subtext{Myriad Neuroscience \hfill Mason, Ohio}
\begin{zitemize}
\item Implemented new features in C\#, JavaScript, and SQL.
\item Replaced Aspose PDF report generation with HTML to PDF conversion to reduce report storage footprint by 18x.
\item Updated and implemented new SQL queries within GeneSight to improve performance and add features.
\item Presented new and updated features to stakeholders for acceptance testing.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{{Software Development Intern \hfill JAN 2016 --- MAY 2016}}
\subtext{Medacheck \hfill Cincinnati, Ohio}
\begin{zitemize}
\item Contributed to Python backend and Android applications for tablet and phone.
\item Developed web and Android applications on Linux platforms.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{{Software Development Intern \hfill AUG 2015 --- JAN 2016}}
\subtext{Strap \hfill Cincinnati, Ohio}
\begin{zitemize}
\item Designed unit tests in Go for data intelligence platform.
\item Performed testing on various services for data intelligence platforms.
\item Developed applications and tests for Linux based platforms.
\end{zitemize}

%====================
% EXPERIENCE F
%====================
\subsection{{Software Engineering Co-Op \hfill JAN 2014 --- JAN 2015}}
\subtext{Myriad Neuroscience \hfill Mason, Ohio}
\begin{zitemize}
\item Contributed features and patches to the GeneSight informatics platform.
\item Performed regression and other QA testing for GeneSight releases.
\item Designed new automated tests for GeneSight continuous integration.
\item Worked on implementation of high availability for GeneSight.
\item Developed SQL Queries and schema for GeneSight databases.
\end{zitemize}

%====================
% EXPERIENCE G
%====================
\subsection{{Research Co-Op \hfill MAY 2013 --- AUG 2013}}
\subtext{Cinicnnati Children's Hospital Medical Center \hfill Cincinnati, Ohio}
\begin{zitemize}
\item Developed Perl application for analysis of large genetic data sets.
\item Tested Perl applications on Linux super compute cluster at Cincinnati Children's
\item Presented findings and developed applications to superiors
\end{zitemize}
